---
title: "30-feature-learning"
output: html_notebook
---


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

Description:
A data frame with 20050 observations on 26 variables, each observation is one day.
Here is the official description: this data set was used to train a CrowdFlower AI gender predictor. Contributors were asked to simply view a Twitter profile and judge whether the user was a male, a female, or a brand (non-individual). The dataset contains more than 20,000 rows, each with a user name, a random tweet, account profile and image, location, and even link and sidebar color.

The problem: 
Here are a few questions we might try to answer with this dataset:

how well do words in tweets and profiles predict user gender?
what are the words that strongly predict male or female gender?
how well do stylistic factors (like link color and sidebar color) predict user gender?


2. Read in and check data
```{r data structure}
str(gender_class)
head(gender_class)
dim(gender_class)
summary(gender_class)
```

```{r check }
colnames(gender_class)[1] <- "unit_id"
colnames(gender_class)[2] <- "golden"
colnames(gender_class)[3] <- "unit_state"
colnames(gender_class)[4] <- "trusted_judgments"
colnames(gender_class)[5] <- "last_judgment_at"

head(gender_class)
```

```{r check NA}
for(col in names(gender_class)) {
  gender_class %>% 
    assert(not_na, col)
}

# Output shown that NA exists here for columns.
```


```{r check duplicate in ID}
length(unique(gender_class$unit_id)) 
# unique() keeps only unique elements, here the length is 20050 which is the same as we know from the data's description. Therefore, there is no duplicate in ID.
```

```{r check the data}
gender_class%>% # check the limit (based on description) for each variable 
  assert(in_set(c("TRUE", "FALSE")), golden)%>% 
  assert(in_set(c("finalized", "golden")), unit_state)%>%
  assert(in_set(c("male", "female","brand")), gender)%>%
  assert(within_bounds(0,1),`gender:confidence`) %>%
  assert(within_bounds(0,1),`profile_yn:confidence`)%>%
  assert(within_bounds(0,Inf),`fav_number`)%>%
  assert(within_bounds(0,Inf),`retweet_count`)%>%
  assert(within_bounds(0,Inf),`tweet_count`)
  
# According to the description, the variable gender contains one of male, female, or brand (for non-human profiles). However, here it has another type of records as "unknown".
```



2. Clean up the data. 

```{r clean the data}
# 0 in hex value should be having six digits, so here I changed it.
gender_class%>%
  mutate(sidebar_color = replace(sidebar_color, sidebar_color == "0", "000000"))
```

```{r clean the data}
# value for gender_gold is all NA.
length(is.na(gender_class$gender_gold) == TRUE)
# value for profile_yn_gold is all NA. Whether the profile y/n value is golden.
length(is.na(gender_class$profile_yn_gold) == TRUE)
# Here, we see that values are all NA for these two variables.
```

```{r clean the data}
# Here we try to replace replace unknown with NA under the variable of gender.
gender_class %>% 
  mutate(gender=ifelse(gender=="unknown",NA,gender))
```


*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 


5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 
