---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5
```{r needed packages}
library(tidyverse)
library(lubridate)
library(RVerbalExpressions)
```


Create a vector of dates giving the first day of every month in the current year.
```{r return first day of every month in the current year}
# 
floor_date(today(),unit = "year")+months(0:11)
```


Write a function that given your birthday (as a date), returns how old you are in years.
```{r return age}
age <- function(bday) {
  (bday %--% today()) %/% years(1)  # 28.9 if use "/"
}                                   # %/% seconds() then will count seconds from bday to today
age(ymd("1995-8-7"))
```



Write a function that given your birthday, returns the day of the week you were born on. 

```{r return the day}
week_born <- function(bday) {
  wday(bday, label = TRUE)
}                                   
week_born(ymd("1995-8-7"),)
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r return seven or more letters}
# regular expression
str_view(stringr::words, "^.{7,}$", match = TRUE)


# RverbalExpression
seven_more <- rx() %>% 
  rx_start_of_line() %>% 
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  rx_end_of_line() %>% 
  print()

str_view(stringr::words,seven_more, match = TRUE)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
Answer: "by"  "dry" "fly" "mrs" "try" "why"
```{r return words that contain consonants}
# regular expression
words[str_detect(stringr::words, "^[^aeiou]+$")]


# RverbalExpression
find_consonants <- rx() %>% 
  rx_start_of_line() %>% 
  rx_anything_but("aeiou") %>% 
  rx_end_of_line()

words[str_detect(stringr::words, find_consonants)]
```


Empirically verify the rule “i before e except after c”.
Answer: for the regular expression and Rverbal, two words break the rule; these words are "science" and "society".
```{r verify i before e except after c}
# Regular Expression
words[str_detect(stringr::words, "cie")]

# RverbalExpression
rule <- rx() %>% 
  rx_anything_but("c") %>% 
  rx_find("cie") %>% 
  print()

words[str_detect(stringr::words, rule)]
```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
# Regular Expression:
x <- c("123-456-7890", "1235-2351","123.456.7890")
# RverbalExpression
telephone <- rx() %>%
  rx_start_of_line() %>%
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-. ") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print()

str_view(x,telephone)
```


